Supplementary material

### 2017-10-12 Manuscript/supplement.tex
Adding figures to supplement.

>>>>

\newpage

\section*{Supplemental figures}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS1.eps}
\caption{
Posterior estimates of process noise forcing the harmonic oscillators for mosquito mortality (A) and growth (B) rates.  Median posterior estimate (black line) and 80\% credible interval (gray band).
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS2.eps}
\caption{
Posterior distribution of process noise variances for mosquito mortality (A) and growth (B) rates.
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS3.eps}
\caption{
Posterior distribution of epidemiological parameters.  The black line indicates the prior mean, as set from the literature.  A: latent period in human host ($1/\rho$), in weeks. B: rate of infectious decay in human host ($\gamma$) in weeks $^{-1}$. C: period of cross-immunity ($1/\delta$) in weeks.
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS4.eps}
\caption{Posterior distribution of initial conditions. A: initial proportion of the human population that is susceptible. B: initial number of exposed individuals. C: initial number of infectious individuals.
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS5.eps}
\caption{Posterior check of autocorrelation structure in the case reports (A) and trapped mosquitoes (B) time series.  Points indicate the observed autocorrelation at the given lag, and vertical lines give the 80\% posterior credible interval of the autocorrelation in the estimated time series.
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS6.eps}
\caption{
Posterior distribution of the total number of cases reported (A) and the total number of mosquitoes captured (B).  Thick line indicates the observed totals.
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS7.eps}
\caption{
Posterior distributions of the minimum and maximum weekly reported cases and trapped mosquitoes. Thick line indicates the observed minima and maxima.
}
\end{figure}

\begin{figure}[!h]
\includegraphics[angle = 270, scale = 1]{figures/figS8.eps}
\caption{
Estimated number of (reported) cases prevented by larval control (i.e decreasing the birth rate, $b_t = r_t + d_t$, by 5\%) applied in a given week. Posterior median (black line) and 80\% credible interval (gray band). Note that this is almost identical to the results from adult control.
}
\end{figure}
